Demographic costs of sexually antagonistic polymorphism in outcrossers and simultaneous hermaphrodites

### 2021-05-03 doc/SA-Hermaphrodites-wDemography.tex
Minor Edits
Honestly, don't remember what this commit does. Minor changes to
the MS.

Fitness trade-offs that impose genetic constraints on adaptation have particularly interesting evolutionary consequences. On the one hand, they prevent individuals (or classes of individuals) from reaching their phenotypic optimum in one or more fitness components, which can increase a population's overall extinction risk \citep{kokko2003sexy,harts2014demography}. On the other hand, they provide an effective mechanism for the maintenance of genetic variation, which influences a population's capactiy for future adaptation \citep{Fisher1930, CharlesworthHughes2000, ConnallonHall2018, MatthewsConnallon2019}. Hence, for traits under conflicting selection, the nature and extent of genetic variation observed in natural populations should reflect a balance between the maintainance of genetic polymorphisms, and the population dynamical consequences of the resulting maladaptation.

>>>>

Fitness trade-offs that impose genetic constraints on adaptation have particularly interesting evolutionary consequences. On the one hand, they prevent individuals (or classes of individuals) from reaching their phenotypic optimum in one or more fitness components, which can increase a population's overall extinction risk \citep{kokko2003sexy,harts2014demography}. On the other hand, they provide an effective mechanism for the maintenance of genetic variation, which influences a population's capacity for future adaptation \citep{Fisher1930, CharlesworthHughes2000, ConnallonHall2018, MatthewsConnallon2019}. Hence, for traits under conflicting selection, the nature and extent of genetic variation observed in natural populations should reflect a balance between the maintainance of genetic polymorphisms, and the population dynamical consequences of the resulting maladaptation.
